\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2020-04-27 ase20/conclusion.tex
[ASE] Revised Realted Work and Conclusion

\section{Conclusion}\label{sec:conclude}
The annual updates of the ECMAScript makes it difficult to
build program analysis or formal verification of JavaScript due to the
required human efforts in modeling a moving target.  In this paper,
we proposed a tool \( \tool \), which \textit{automatically} extracts the
syntax and semantics specified in ECMAScript.  The tool
generates a parser from a language grammar written in \( \bnfes \), and
compiles abstract algorithms written in English to \( \ires \) functions.
The only parts that require manual efforts are compile rules and
language-specific global setting, which we provide for ECMAScript
as an example case study.  We also support \textsf{Fault Localizer} to
adapt updates of ECMAScript by suggesting new rules.
We evaluated \( \tool \) by applying it to ES10 with Test262.
The extracted semantics passed 19,220 of 19,282 applicable tests in Test262.
The tool also detected three confirmed errors from the specification.
Moreover, we showed that the tool is also applicable to an incomplete
language proposal. The implementation of the tool is publicly available
as an open-source project.

>>>>

\section{Conclusion}\label{sec:conclude}

The annual updates of the ECMAScript makes it difficult to build program
analysis or formal verification of JavaScript due to the required human efforts
in modeling a moving target.  In this paper, we proposed a tool \( \tool \),
which \textit{automatically} extracts the syntax and semantics specified in
ECMAScript.  The tool generates a parser from a language grammar written in \(
\bnfes \), and an AST-IR translator from abstract algorithms written in
English.  The tool automatically extract all syntax and \inred{XX.XX\%} of
semantics for the most recent four versions of ECMAScript (ES7 to ES10).  We
evaluated the correctness of the tool by testing the extracted semantics from
ES10 with Test262, the official conformance suite.  Based on \inred{X,XXX}
failed tests, we found eight specification errors in ES10. After resolving
them, the extracted semantics passed all \inred{XX,XXX} applicable tests.
Moreover, we showed that \( \tool \) is also forward compatible for the future
language features by applying it to nine proposals, and we found four
specification errors in the proposal for BigInt.  We believe that it could
dramatically reduce the human efforts to define formal semantics of ECMAScript
and also bridge gaps between ECMAScript and Test262.

### 2020-04-27 ase20/related.tex
[ASE] Revised Realted Work and Conclusion

From Packrat parsing~\cite{packrat} with PEG~\cite{peg}, recursive-descent
parsers with backtracking support linear-time parsing.  However, it
has the fundamental problem of ordered choices: \( ab \) is silently
unmatched with \( a \mid ab \).  While Generalized LL (GLL) parsing~\cite{gll}
is basically recursive-descent with backtracking that can support general
context-free grammars (CFGs) even in the presence of ambiguous grammars,
its worst-time complexity is \( O(n^3) \) for the input size \( n \).
Unlike GLL parsing, our lookahead parsing is not applicable to general CFGs,
but we experimentally showed that it can generate JavaScript parsers.
The complexity of lookahead parsing is \( O(k \cdot n) \) for the input size
\( n \) and the constant number of tokens \( k \).

In the field of automatic model generation, the closest related work to
ours is \citet{javadoc}'s, which generates Java code from Javadoc comments
for API functions.  Using NLP techniques and various heuristic methods,
it produces several candidate code tests them with actual implementation
of the API functions to find correct modeling.  Unlike their approach, we
introduce a fault localization algorithm to support future language
updates and to provide correct meaning of specification. Our tool is also
applicable for testing even when the actual implementation is not available.

% TODO pseudo code의 형태와 natural language의 결합이다.
% TODO moudular test로 guide를 받을 수 없어서 user defined rule을 사용. 대신, statistical analysis를 기반으로 guide해줌

% \begin{itemize}
%   \item Automatic Model Generation from Documentation for Java API Functions (ICSE'16)~\cite{javadoc}
% \end{itemize}

% Building formal semantics of language is important for program verification and static analysis. JavaScript is most widely-used language in
% web browser, but its complex behavior makes confusion to developer and program analysis designer. So there are many researches to define formal semantics of JavaScript and
% using it to formal verification or program analysis.

Several approaches have defined the formal semantics of JavaScript.
\citet{lambdajs} defined a core calculus of JavaScript, and expressed the
rest as desugaring.  While it presents the core JavaScript semantics in
an extension of the $\lambda$ calculus, it does not show the semantics
correspondence defined in ECMAScript.  KJS~\cite{kjs} and
JaVerT~\cite{javert} defined formal semantics of JavaScript by manually converting
ECMAScript to their own formal languages.  KJS mapped
ES5.1 in the K framework~\cite{kframework}, which can be used
for program verification and analysis.  Similarly, JaVerT converts the
specification to their own IR called JSIL to make further analysis.
Our approach provides a mechanized framework to synthesize syntactic parsers and
to automatically extract semantics
using a rule-based compilation technique, which significantly reduces human
efforts.

% \begin{itemize}
%   \item JaVerT: JavaScript verification toolchain (POPL'18)~\cite{javert}
%   \item KJS: A complete formal semantics of JavaScript (PLDI'15)~\cite{kjs}
%   \item The Essence of JavaScript (ECOOP'10)~\cite{lambdajs}
%   \item A Trusted Mechanised JavaScript Specification (POPL'14)~\cite{jscert}
% \end{itemize}

>>>>

From Packrat parsing~\cite{packrat} with PEG~\cite{peg}, recursive-descent
parsers with backtracking support linear-time parsing.  However, it
has the fundamental problem of ordered choices: \( ab \) is silently
unmatched with \( a ~/~ ab \).  While Generalized LL (GLL) parsing~\cite{gll}
is basically recursive-descent with backtracking that can support general
context-free grammars (CFGs) even in the presence of ambiguous grammars,
its worst-time complexity is \( O(n^3) \) for the input size \( n \) and it
does not support context-sensitive features.  Unlike GLL parsing, our lookahead
parsing is applicable for JavaScript parsers having context sensitive features
such as positive/negative lookaheads. Moreover, The complexity of lookahead
parsing is \( O(k \cdot n) \) for the input size \( n \) and the constant
number of tokens \( k \). We experimentally showed that it can generate parsers
for the most recent four versions of ECMAScript.

In the field of automatic model generation, the closest related work to
ours is \citet{javadoc}'s, which generates Java code from Javadoc comments
for API functions.  Using NLP techniques and various heuristic methods,
it produces several candidate code tests them with actual implementation
of the API functions to find correct modeling.  Unlike their approach, we
introduce semi-automatic synthesis based on general compile rules that
represent the common writing patterns to support future language updates and to
provide correct meaning of specification.  The extracted semantics via our tool
is also executable that helps to bridge gaps between the specification written
in a natural language and tests.

Several approaches have defined the formal semantics of JavaScript.
\citet{lambdajs} defined a core calculus of JavaScript, and expressed the
rest as desugaring.  While it presents the core JavaScript semantics in
an extension of the $\lambda$ calculus, it does not show the semantics
correspondence defined in ECMAScript.  KJS~\cite{kjs} and
JaVerT~\cite{javert} defined formal semantics of JavaScript by manually converting
ECMAScript to their own formal languages.  KJS mapped
ES5.1 in the K framework~\cite{kframework}, which can be used
for program verification and analysis.  Similarly, JaVerT converts the
specification to their own IR called JSIL to make further analysis.
However, all of them targets only ES5.1 or former versions of ECMAScript and
they do not provide solution for annual updates of ECMAScript. Our approach
provides a mechanized framework to synthesize JavaScript parsers and to
automatically extract semantics using a rule-based compilation technique, which
significantly reduces human efforts.
